Title

### 2016-11-24 paper.tex
Modified biblio

%\section{Kernel for structures and Multiple Kernel Learning}
\section{Backgroung}
When dealing with structured data, the choice of the kernel to adopt is a key step. Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between predictive performance and computational time (of course, this trade-off depends from the considered task).
In this paper we focus on graphs, i.e. we consider each example to be a different graph.
In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima2003,Mah'e2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Borgwardt2005} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\citep{Shervashidze2009} . The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
Recently, different almost linear time graph kernels have been defined in literature \citep{Heinonen2009,Shervashidze2009a,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
In the following we will give some details about the considered alternatives.
\textcolor{red}{TODO}\\
\begin{itemize}
 \item WL
 \item NSPDK
 \item ODD$_{ST}$
\end{itemize}

@@

\bibliographystyle{unsrt}
\bibliography{donini,biblio}

>>>>

%\section{Kernel for structures and Multiple Kernel Learning}
\section{Backgroung}
When dealing with structured data, the choice of the kernel to adopt is a key step. Depending on the type of data under consideration, different proposals are available in literature, each one with a different trade-off between predictive performance and computational time (of course, this trade-off depends from the considered task).
In this paper we focus on graphs, i.e. we consider each example to be a different graph.
In this case, there are several graph kernels defined in literature based on random walks~\cite{Kashima03marginalizedkernels,Mahe2004} ($O(n^3)$ computational complexity), shortest paths~\cite{Kriegel05shortestpath} ($O(n^4)$ computational complexity), subgraphs up to a fixed size~\cite{Shervashidze2009} . The problem with these kernels is the high computational complexity, that makes them inapplicable to several real-world datasets.
Recently, different almost linear time graph kernels have been defined in literature \cite{Heinonen2009,NIPS2009_0533,Costa2010,Shervashidze2011,Dasan2012,DaSanMartino2016}, and these are the ones we focus o in this paper.
In the following we will give some details about the considered alternatives.
\textcolor{red}{TODO}\\
\begin{itemize}
 \item WL
 \item NSPDK
 \item ODD$_{ST}$
\end{itemize}

@@

\bibliographystyle{unsrt}
\bibliography{donini,biblio,Mendeley}
